### 2019-02-14 manuscript/methods.tex
more editing Methods

As a third approach, we analyzed the roles of both polyploidy and breeding system in the process of diversification using a multivariate speciation and extinction model (MuSSE, \citet{fitzjohn_2012}).  We named our MuSSE the ID/P/CD breeding system and polyploidy model, where the three states are self-incompatible diploids (ID), polyploids (always self-compatible, P=1), and self-compatible diploids (CD). The model is defined via ten parameters; six defining diversification ($\lambda_{CD}, \mu_{CD},\lambda_{P},\mu_{P}, \lambda_{ID},\mu_{ID}$) and  four parameters defining key trait changes: polyploidization of self-compatible diploids $\rho_{C}$, diploidization $\delta$, polyploidization of self-incompatible diploids $\rho_{I}$, and self-incompatible to self-compatible rate $q_{IC}$.

% E: lack of SI-P is now mentioned in Data and should be explained in Intro: Fixed in data still needs to be mentioned in intro

Since the null hypothesis of the MuSSE model is that the diversification is equal and constant for all three states defined, it is possible that MuSSE can also suffer from large type I errors as their BiSSE equivalents. Therefore. we extended MuSSE model to account for a hidden state like the methodology recently proposed by \citet{caetano_2018} and \citet{herrera_2018}. A full fitted MuHiSSE model would have 26 parameters total \citep{herrera_2018}. Since our goal was to look for diversification rate differences polyploidy and breeding system rather than differences occurring at  hidden state, we fitted a simplified version, the  ID/P/CD-A/B model, that is defined via16 parameters. The reduction in parameter space is achieved by fixing the rates amongst hidden states to be equal with parameter $\alpha$ and fixing the transition rates amongst breeding system to be the same as  the ones defined in the MuSSE model ($\rho_{ID}$,  $\delta$,  $\rho_{CD}$,  $q_{IC}$) independently from the hidden state.   Therefore, the ID/P/CD- A/B model was used to estimate twelve speciation and extinction rates ($\lambda_{ID_A}, \mu_{ID_A},\lambda_{P_A},\mu_{P_A}, \lambda_{CD_A},\mu_{CD_B},\lambda_{ID_B}, \mu_{ID_B},\lambda_{P_B},\mu_{P_B}, \lambda_{CD_B},\mu_{CD_B}$), and the net diversification and relative extinction rates associated with them.\newline

@@

\subsection{Statistical Inference under the models}

>>>>

If both ploidy and breeding system have the potential to influence lineage diversification, we should logically consider their effects jointly.
We thus fit a model that includes both traits \citep[MuSSE,][]{fitzjohn_2012}.
The three states in this model are self-incompatible diploids (ID), self-compatible diploids (CD), and polyploids, which are always self-compatible (CP).
We did not include a state for self-incompatible polyploids because they are not present in the data, and because that trait combination is logically expected not to occur (as explained above).
We call this the $ID/CD/CP$ ploidy and breeding system model.
It has ten parameters, six for diversification in each state ($\lambda_{ID},\ \lambda_{CD},\ \lambda_{CP}$ for speciation, $\mu_{ID},\ \mu_{CD},\ \mu_{CP}$ for extinction) and four for transitions between states ($\rho_I,\ \rho_C$ for polyploidization transitions from $ID$ and $CD$ to $CP$, respectively; $\delta$ for diploidization from $CP$ to $CD$; $q_{IC}$ for loss of self-incompatibility without polyploidization, from $ID$ to $CD$).
The total rate of loss of self-incompatibility, \ie transitions out of $ID$, is $q_{IC} + \rho_I$.
Diploidization from $CP$ to $ID$ is not allowed because it would be a regain of self-incompatibility.

The $ID/CD/CP$ model could potentially capture similar dynamics as earlier models, if the hidden state in $D/P-A/B$ was effectively breeding system, and the hidden state in $I/C-A/B$ was effectively ploidy.
There is also the potential, however, for a hidden factor to be influencing diversification even beyond both of our focal traits, and this could again mislead inferences.
We therefore added a hidden trait layer on top of our three-state model \citep[analogous to][]{caetano_2018, herrera_2018, huang_2018}.
We refer to this as the $ID/CD/CP-A/B$ model.
A fully parameterized version of this model would have 26 rate parameters \citep{herrera_2018}. 
Because our goal was to look for diversification rate differences associated with ploidy and breeding system rather than the specific effects of the hidden states, we fitted a simplified version with 16 parameters.
The reduction in parameter space is achieved by fixing the rates for transitions among hidden states to be equal with rate $\alpha$, and fixing the transition rates between observed states to be independent of the hidden state (rates $\rho_I,\ \rho_C,\ \delta,\ q_{IC}$ as defined for the $ID/CD/CP$ model).
There are additionally twelve diversification rate parameters ($\lambda_{ID_A},\ \lambda_{ID_B},\ \lambda_{CD_A},\ \lambda_{CD_B},\ \lambda_{CP_A},\ \lambda_{CP_B},\ \mu_{ID_A},\ \mu_{ID_B},\ \mu_{CD_A},\ \mu_{CD_B},\ \mu_{CP_A},\ \mu_{CP_B}$).

@@

\subsection{Statistical inference under the models}
